SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-03 2017-Xudong-SMT/ActaInformatica.tex

Implementing these semantics raised several challenges:
\begin{itemize}
	\item to obtain a tool that could be applied to pNets representing
	various languages, in particular various action algebras,
	with their specific decision theories;
	\item \QIN{to separate clearly the
	transitions of a generated open automaton from the
	combination of all possible (symbolic) behaviours, and from
	the symbolic reasoning part, specifically here, to check the
	satisfiability of the predicates in the transitions generated by our algorithm using an SMT
	engine;}
	\item to build a prototype of the algorithm, and validate the approach on our basic
	case-studies, meanwhile, understand the efficiency of the interaction
	with the SMT solver.
\end{itemize}

@@

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}.
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the 
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} how to prove that they are bisimilar.

>>>>

Implementing these semantics raised several challenges:
\begin{itemize}
	\item to obtain a tool that could be applied to pNets representing
	various languages, in particular various action algebras,
	with their specific decision theories;
	\item to separate clearly the 
	algorithm 
	\YX{that generates the transitions of an open automaton from
	the symbolic reasoning part that uses an SMT
	engine to check the
	satisfiability of the predicates generated by the algorithm;}

%	\item to separate clearly the algorithm generating the transitions of an open automaton from combination of all possible (symbolic) behaviours, and from the symbolic reasoning part, specifically here using an SMT engine to check the satisfiability of the predicates generated by our algorithm;
	\item to build a prototype of the algorithm, and validate the approach on our basic
	case-studies, meanwhile, understand the efficiency of the interaction
	with the SMT solver.
\end{itemize}

@@

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}.
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the 
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} 
\YX{that the two open automata are equivalent with respect to a notion of FH-bisimulation.}
%how to prove that they are bisimilar.
